Results

### 2025-04-03 notebooks/00_index.qmd
feat: overview plot

```{julia}
using Speasy
speasy()

using DimensionalData
using SpaceTools
using GLMakie
using Dates
```

```{julia}
tmin = DateTime("2021-04-29")
tmax = DateTime("2021-04-30")

density_tvar = SpaceTools.DataSet(
    "Density",
    [
        "cda/PSP_SWP_SPI_SF00_L3_MOM/DENS",
        "cda/PSP_FLD_L3_RFS_LFR_QTN/N_elec",
        "cda/PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"
    ]
)

# tvars_psp = [
#     "cda/PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc",
#     density_tvar,
#     "cda/PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN",
#     "cda/PSP_SWP_SPI_SF00_L3_MOM/TEMP",
# ]

tvars_wind = [
    "cda/WI_H2_MFI/BGSE",
    ["cda/WI_PM_3DP/P_DENS" "cda/WI_PM_3DP/P_TEMP"],
    "cda/WI_PM_3DP/P_VELS",
]

f = Figure()
add_title = true
# tplot(f[1, 1], tvars_psp, tmin, tmax; add_title)
tplot(f[1, 2], tvars_wind, tmin, tmax; add_title)
add_labels!()
f
```

>>>>

WI_H1_SWE	Proton_W_moment	        Proton thermal speed W (km/s) from isotropic moment analysis
WI_H1_SWE	Proton_Wperp_moment 	Proton thermal speed Wperpendicular (km/s) from bimax moment analysis
WI_H1_SWE	Proton_Wpar_moment	    Proton thermal speed Wparallel (km/s) from bimax moment analysis

WI_H1_SWE	Proton_Wperp_nonlin	    Proton thermal speed perpendicular to the magnetic field direction [km/s].
WI_H1_SWE	Proton_Wpar_nonlin	    Proton thermal speed parallel to the magnetic field direction [km/s].

```{julia}
using Speasy
using SPEDAS
using SPEDAS: ulabel
using DimensionalData
using GLMakie
# using CairoMakie
using Dates
using PartialFunctions
using Unitful, Latexify, UnitfulLatexify, LaTeXStrings
using Beforerr: _theme_legend

update_theme!(_theme_legend(; padding=(0, 0, 0, 0)))
```

```{julia}
tmin_psp = DateTime("2021-01-14")
tmax_psp = DateTime("2021-01-21")
tmin_wind = DateTime("2021-01-15")
tmax_wind = DateTime("2021-01-23")

tmin_psp = DateTime("2021-01-14")
tmax_psp = DateTime("2021-01-15")
tmin_wind = DateTime("2021-01-17")
tmax_wind = DateTime("2021-01-18")

B_ylabel = "B (nT)"
B_labels = ["Bx", "By", "Bz", "Magnitude"]
V_ylabel = "Velocity (km/s)"
V_labels = ["Vx", "Vy", "Vz", "Magnitude"]
Temp_ylabel = "Temperature (eV)"
WI_PM_3DP_labels = ["Proton"] # "Proton (3DP, PESA Low)"
WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"

psp_n = SPEDAS.DataSet(
    "Density",
    [
        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/DENS"; labels=["SPI Proton"]),
        SpeasyProduct("PSP_FLD_L3_RFS_LFR_QTN/N_elec"; labels=["RFS Electron"]),
        SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"; labels=["SQTN Electron"])
    ];
    ylabel=ulabel("Density", "cm^-3")
)

psp_temp = SPEDAS.DataSet(
    "Temperature",
    [
        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/TEMP"; labels=["SPI Proton"]),
        SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_core_temperature"; labels=["SQTN Electron core"]),
    ];
    ylabel=Temp_ylabel
)

tvars_psp = [
    tnorm_combine ∘ SpeasyProduct("PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc"; ylabel=B_ylabel, labels=B_labels),
    psp_n,
    SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN"; ylabel=V_ylabel, labels=V_labels),
    psp_temp,
]

wind_n = SPEDAS.DataSet(
    "Density",
    [
        SpeasyProduct("WI_PM_3DP/P_DENS"; labels=WI_PM_3DP_labels),
        SpeasyProduct("WI_ELM2_3DP/DENSITY"; labels=WI_ELM2_3DP_labels)
    ];
    ylabel=ulabel("Density", "cm^-3")
)

wind_temp = SPEDAS.DataSet(
    "Temperature",
    [
        SpeasyProduct("WI_PM_3DP/P_TEMP"; labels=WI_PM_3DP_labels),
        SpeasyProduct("WI_ELM2_3DP/AVGTEMP"; labels=WI_ELM2_3DP_labels),
    ];
    ylabel=Temp_ylabel
)

tvars_wind = [
    tnorm_combine ∘ SpeasyProduct("WI_H3-RTN_MFI/BRTN"; ylabel=B_ylabel, labels=B_labels),
    wind_n,
    SpeasyProduct("WI_K0_SWE_RTN/V_RTN"; ylabel=V_ylabel, labels=V_labels),
    wind_temp,
    SPEDAS.DataSet("Thermal speed", ["WI_H1_SWE/Proton_Wperp_nonlin", "WI_H1_SWE/Proton_Wpar_nonlin", "WI_H1_SWE/Proton_Wperp_moment", "WI_H1_SWE/Proton_Wpar_moment"]),
    "WI_ELM2_3DP/MAGT3"
]

tvars_themis = [
    tnorm_combine ∘ SpeasyProduct("THB_L2_FGM/thb_fgs_gseQ"; ylabel=B_ylabel, labels=B_labels),
    ["THB_L2_MOM/thb_peim_densityQ", "THB_L2_MOM/thb_peem_densityQ"],
    SpeasyProduct("THB_L2_MOM/thb_peim_velocity_gseQ"; ylabel=V_ylabel, labels=V_labels),
    "THB_L2_ESA/thb_peif_avgtempQ",
    SpeasyProduct("THB_L2_MOM/thb_peim_t3_magQ"; yscale=identity),
    SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; yscale=identity),
]

f = Figure(; size=(1200, 800))
add_title = false
legend = (; position=Top())
tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; add_title, legend)
tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; add_title, legend)
tplot(f[1, 3], tvars_themis, tmin_wind, tmax_wind; add_title, legend)
add_labels!(f[1, 1]; labels='1':'9', open="(a.")
add_labels!(f[1, 2]; labels='1':'9', open="(b.")
add_labels!(f[1, 3]; labels='1':'9', open="(c.")
f
```
